Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-07 paper/sec-analysis.tex
work on the paper

  In addition to the basic $p_T$ and $\eta$
  acceptance requirements, large-$R$ jets should also
  satisfy the  BDRS mass-drop tagger~\cite{Butterworth:2008iy}
  conditions, in order
  to enhance the discrimination of the signal over the background
  events.
  %
  For the BDRS mass-drop tagger, we use the {\tt FastJet} default
  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.
  %
  As required, before the mass-drop tagger is applied, the large-$R$ jet
  constituents are reclustered with the Cambridge/Aachen
  algorithm.

@@

\subsection{Event categorisation and cut flow}

@@

Once a pair of Higgs boson candidates has been identified,
then events from each category are required to satisfy the usual
Higgs mass window cut, defined by
the following condition
\be
|m_{h,j} - 125| < 40~{\rm GeV} \, , j=1,2 \, ,
\ee
where $m_{h,j}$ is the invariant mass of the two Higgs candidates
reconstructed as explained above.
%
We note that this cut is substantially looser as the corresponding
cut used in the typical ATLAS and CMS $h\to b\bar{b}$
analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}: the motivation
for this is that the MVA will take care of the optimisation of these
and other cuts that are not explicitly performed.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \small
  \begin{tabular}{c|c|c|c}
    \hline
    &  Boosted  &  Intermediate  &  Resolved  \\
    \hline
    \hline 
    Jet selection  &  $\ge 2$ large-$R$ jets  & 1 large-$R$ jet, $\ge 2$ small-$R$
    jets  &  $\ge$ 4 small-$R$ jets \\
    \hline
    Jet cuts  & $p_T \ge 200$ GeV   &  $p_T \ge 200$ GeV (large-$R$ jet)
    &  $p_T \ge 40$ GeV \\
    &  & $p_T \ge 40$ GeV (small-$R$ jets)   &    \\
    &   $|\eta|<2.0$  & $|\eta|<2.0$ (large-$R$ jet) & $|\eta|<2.5$ \\
    &        & $|\eta|<2.5$ (small-$R$ jet)  &  \\
    \hline
    $b$-tagging  & 2 double-$b$-tags  & 1 double-$b$-tag & 4 single-$b$-tags \\
    &  & and 2 single-$b$-tags  &  \\
       & $\ge 2$ small-$R$ subjets  & &  \\
    &  $p_T^{\rm sj}\ge 50$ GeV &   &  \\
    \hline
    \end{tabular}
  \caption{\small Definition of the three event categories used in this
    work, together with the corresponding basic kinematical cuts.
    %
    The categories are not exclusive, and each event can satisfy the
    requirements of more than one category at the same time.  
\label{sec:categorisation}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As we will show now, the selection requirement and the kinematic cuts
for each of the categories in Table~\ref{sec:categorisation} have
been optimised independently.
%
First of all we have performed a inclusive analysis, and optimised
$S/\sqrt{B}$ in each of the three categories separately, including
the MVA.
%
We find that, in terms of signal significance, the ordering of
the categories is
\begin{enumerate}
\item Boosted 
\item Intermediate
  \item Resolved
  \end{enumerate}
and therefore for the final analysis we turn to an exclusive approach:
if an event satisfies the boosted requirements, it is kept for
these category, else we check if it suits the intermediate
requirements, and failing also this, the event is attempted
in the resolved categories.
%
The resulting exclusive event samples are then separately processes
through the MVA, as discussed in the next section.
%
This allows us to combine the significance of the dominant topology
(boosted) with that of the sub-leading categories, intermediate
and resolved.

>>>>

  In addition to the basic $p_T$ and $\eta$
  acceptance requirements, large-$R$ jets should also
  satisfy the  BDRS mass-drop tagger~\cite{Butterworth:2008iy}
  conditions, in order
  to enhance the discrimination of the signal over the background
  events.
  %
  For the BDRS mass-drop tagger, we use the {\tt FastJet} default
  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.
  %
  As required, before the mass-drop tagger is applied, the large-$R$ jet
  constituents are reclustered with the Cambridge/Aachen
  algorithm~\cite{Dokshitzer:1997in,Wobisch:1998wt}.

@@

\subsection{Event categorisation and cut flow}
\label{sec:categorisation}

@@

Once a pair of Higgs boson candidates has been identified,
then events from each category are required to satisfy the usual
Higgs mass window cut, defined by
the following condition
\be
\label{higgsmasswindow}
|m_{h,j} - 125| < 40~{\rm GeV} \, , j=1,2 \, ,
\ee
where $m_{h,j}$ is the invariant mass of the two Higgs candidates
reconstructed as explained above.
%
We note that this cut is substantially looser as the corresponding
cut used in the typical ATLAS and CMS $h\to b\bar{b}$
analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}: the motivation
for this is that the MVA will take care of the optimisation of these
and other cuts that are not explicitly performed.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \centering
  \small
  \begin{tabular}{c|c|c|c}
    \hline
    &  Boosted  &  Intermediate  &  Resolved  \\
    \hline
    \hline 
    Jet selection  &  $\ge 2$ large-$R$ jets  & 1 large-$R$ jet, $\ge 2$ small-$R$
    jets  &  $\ge$ 4 small-$R$ jets \\
    \hline
    Jet cuts  & $p_T \ge 200$ GeV   &  $p_T \ge 200$ GeV (large-$R$ jet)
    &  $p_T \ge 40$ GeV \\
    &  & $p_T \ge 40$ GeV (small-$R$ jets)   &    \\
    &   $|\eta|<2.0$  & $|\eta|<2.0$ (large-$R$ jet) & $|\eta|<2.5$ \\
    &        & $|\eta|<2.5$ (small-$R$ jet)  &  \\
    \hline
    $b$-tagging  & 2 double-$b$-tags  & 1 double-$b$-tag & 4 single-$b$-tags \\
    &  & and 2 single-$b$-tags  &  \\
       & $\ge 2$ small-$R$ subjets  & &  \\
    &  $p_T^{\rm sj}\ge 50$ GeV &   &  \\
    \hline
    \end{tabular}
  \caption{\small Definition of the three event categories used in this
    work, together with the corresponding basic kinematical cuts.
    %
    The categories are not exclusive, and each event can satisfy the
    requirements of more than one category at the same time.  
\label{sec:categorisationTable}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As we will show now, the selection requirement and the kinematic cuts
for each of the categories in Table~\ref{sec:categorisationTable} have
been optimised independently.
%
First of all we have performed a inclusive analysis, and optimised
$S/\sqrt{B}$ in each of the three categories separately, including
the MVA.
%
We find that, in terms of signal significance, the ordering of
the categories is
\begin{enumerate}
\item Boosted 
\item Intermediate
  \item Resolved
  \end{enumerate}
and therefore for the final analysis we turn to an exclusive approach:
if an event satisfies the boosted requirements, it is kept for
these category, else we check if it suits the intermediate
requirements, and failing also this, the event is attempted
in the resolved categories.
%
The resulting exclusive event samples are then separately processes
through the MVA, as discussed in the next section.
%
This allows us to combine the significance of the dominant topology
(boosted) with that of the sub-leading categories, intermediate
and resolved.

### 2015-07-07 paper/sec-mcsamples.tex
work on the paper

Higgs pair production is simulated at leading order using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, with finite $m_t$ effects taken into
account.\footnote{We thank Eleni Vrodynou for assistance here.}
%
We use the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
$\alpha_S(m_Z^2)=0.118$
as interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
We use the default settings of the renormalization and factorization
scale of the model.
%
The Higgs boson parameters are also the same in the default model,
in particular we use $m_H=125$ GeV, consistent with the latest
measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
%
The value of the Higgs trilinear coupling $\lambda$ is set to its
Standard Model value.
%
The calculation is performed in the
$N_f$=4 scheme and thus
takes into account the finite mass of the $b$-quarks.

>>>>

Higgs pair production is simulated at leading order using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, with finite $m_t$ effects taken into
account.\footnote{We thank Eleni Vrodynou for assistance here.}
%
This tailored {\tt MadGraph5\_aMC@NLO} model  simulates
gluon-gluon-fusion Higgs boson pair production including the effects
of the
exact form factors for the top triangle and box loops at leading
order, obtained from~\cite{Plehn:1996wb}.\footnote{Note that since recently it is possible to compute also
loop-induced processes as well without the need of special
models~\cite{Hirschi:2015iia}.}
%
We use the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
$\alpha_S(m_Z^2)=0.118$
as interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
We use the default settings of the renormalization and factorization
scale of the model.
%
The Higgs boson parameters are also the same in the default model,
in particular we use $m_H=125$ GeV, consistent with the latest
measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
%
The value of the Higgs trilinear coupling $\lambda$ is set to its
Standard Model value.
%
The calculation is performed in the
$N_f$=4 scheme and thus
takes into account the finite mass of the $b$-quarks.

### 2015-07-07 paper/sec-mva.tex
work on the paper

After the traditional cut-based analysis presented in the previous section,
and combining the significance of the different event categories,
we end up with a $S/\sqrt{B}$ value of AAA.
%
Taking into account our more realistic simulation of the QCD background as
compared to previous studies, this is not too bad.
%
however, the attentive reader might have noticed that we have used
relatively 
loose kinematics cuts, for example in the Higgs mass window.
%
The motivation for this is that the $n$-tuples of signal and background
events, after our basic selection, are processed though a multivariate
analysis with the motivation to increase the signal over background
significance.
%
Multivariate techniques are by now a common tool to enhance signal
significance in HEP analysis.

\subsection{MVA strategy}

The classification of events as arising from either signal or
background processes via the use of a multivariate analysis is a common
technique in high energy physics.
%
In order to investigate the potential efficacy of an MVA in an $hh\to 4b$
measurement, we process the events remaining after the cut-based analysis 
through a feed-forward artificial neural network with architecture
\be
\label{eq:nn1}
N_{\mathrm{var}}\times5\times3\times1 \, ,
\ee
where $N_{\mathrm{var}}$ represents the number of input variables for the MVA.
All neural-network layers use a sigmoid activation function, allowing
for a probabilistic
interpretation of the neural-network output.

>>>>

After the traditional cut-based analysis presented in the previous section,
and combining the significance of the different event categories,
we end up with a $S/\sqrt{B}$ value around $1.2$.
%
This is not enough to claim observation in this channel.
%
however, the attentive reader might have noticed that we have used
relatively 
loose kinematics cuts, for example in the Higgs mass window.
%
The motivation for this is that the $n$-tuples of signal and background
events, after our basic selection, are processed though a multivariate
analysis with the motivation to increase the signal over background
significance.
%
Multivariate techniques are by now a common tool to enhance signal
significance in HEP analysis, and rightly so,
since they open a new window to improve the performance
of many physics analysis and searches.
%
For instance, the UCL $hh\to 4b$ analysis~\cite{Wardrope:2014kya}
uses a Boosted
Decision Tree MVA to improve signal discrimination.

\subsection{MVA strategy: deep neural networks}

The classification of events as arising from either signal or
background processes via the use of a multivariate analysis is a common
technique in high energy physics~\cite{Baldi:2014pta,Wardrope:2014kya}.
%
In our work we use a specific type of  MVA to
disentangle signal and background events in the $hh\to 4b$ process,
in particular we use a feed-forward artificial neural network (ANN).
%
The basic idea is that the ANN is given both all MC signal and background
events which satisfy the basic selection cuts {\bf C1}, allowing to identify
which are the most relevant variables to discriminate between the two.

In this work, the ANN that we use has the following architecture.
\be
\label{eq:nn1}
N_{\mathrm{var}}\times5\times3\times1 \, ,
\ee
where $N_{\mathrm{var}}$ represents the number of input variables for the MVA.
All neural-network layers use a sigmoid activation function, allowing
for a probabilistic
interpretation of the neural-network output, including in the final layer.
%
In Fig.~\ref{fig:nnarch} we show an example of the ANN that we use in this work, corresponding here
to the case of the resolved category.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
      \vspace{-1cm}
  \includegraphics[width=0.80\textwidth]{plots/res_nnarch.pdf}
  \vspace{-1cm}
\caption{\small Architecture of the ANN used for the analysis of the resolved
  category, with $N_{\rm var}=13$ input variables and thus the same number of neurons
in the first layer.}
\label{fig:nnarch}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

### 2015-07-07 paper/sec-results.tex
work on the paper

\section{Cut-based analysis results}

@@

In this section we discuss the results of the traditional
cut-based analysis, using the strategy presented in the previous
section.
%
We compare our results with other recent related studies,
and in particular we study how the signal significance
is modified if only the $4b$ QCD background is taken into account,
but the $2b2j$ and $jjjj$ backgrounds are neglected, as done
in previous work.
%
Then in the next section we show how using multivariate techniques
one can substantially improve the signal significance as compared
to the cut-based analysis.

@@

We now study the basic results of our cut based analysis, with
all backgrounds properly taken into account.

We begin by showing the cut-flow at various levels of the analysis.
%
Here we consider all backgrounds at the same time, and below
we comment on the role of the individual backgrounds.

We consider the following levels of the cut-flow
\begin{itemize}
\item {\bf C0}: these are the cross-sections at the generator
  level, before any analysis cuts
\item {\bf C1}: results after the basic jet selection
  and related cuts, but before $b$-tagging.
\item {\bf C2}: results after the $b$-tagging, but
  before applying the invariant mass window cut
\item {\bf C3}: final results of the cut-based
  analysis
  \end{itemize}
We consider the results for the individual categories, using the
exclusive priorisation discussed in the previous section.
%
In Appendix.~\ref{sec:overlap} we comment
interplay of the overlap between the various categories.
%
At each stage of the cut flow, we also provide the number
of events that would be expected at the HL-LHC with
an integrated luminosity of $\mathcal{L}=3000$ fb$^{-1}$,
the signal significance $S/\sqrt{B}$ and the signal
over background ratio $S/B$.
%
Results are shown both for the signal and for all backgrounds
combined.
%
The results for the three categories have been collected in
Table~\ref{table:cutflow}.

We emphasize that it is important not only to achieve a good signal
significance, $S/sqrt{B}$, but also a good signal over background ratio $S/B$:
if the latter is too small, a measurement of the background with an infeasible small
systematic uncertainty would be required.

Let's begin with the discussion of the boosted category, that as we have explained
is the one that benefits from a higher signal significance.
%
We see that after all the cuts, including $b$-tagging,
we end up with almost 200 signal events at the HL-LHC, and
still a substantial background of around $40k$ events.
%
The signal significance is around one at the end of the
cut-based analysis.
%
Note that it is easy to compute the corresponding numbers
for the end of Run II at the LHC with
$\mathcal{L}_{\rm int}=300$ fb$^{-1}$: we have only
19 signal events, and the signal significance drops down to
$S/\sqrt{B}\sim 0.3$.
%
We will discuss in the next section what are the Run II prospects
once we include the effects of the MVA in the analysis.

@@

@@

From the results of Table~\label{table:cutflowboosted}
we see that after the cut-based analysis, the significance of the Higgs pair production
observation in the $4b$ channel using the boosted topology is ... and that the combination
of the boosted, intermediate and resolved categories gives ....
%
We discuss in the next section of this significance can be enhanced by means
of multivariate analysis.

@@

We now compare with two recent studies that have also studied the
feasibility of SM Higgs pair production in the $4b$ final state,
those of the UCL group~\cite{Wardrope:2014kya} and of the
Durham group~\cite{deLima:2014dta}.
%
In order to perform a meaningful comparison, we will only consider
here the $4b$ QCD and $t\bar{t}$ backgrounds, as was done
in these two studies.

{\bf paragraph about UCL strategy}

{\bf paragraph about Durham strategy}

In order to compare with previous results, it is interesting to
study how our results change if we consider only the QCD $4b$
multi-jet background, but ignore the $2b2j$ and $4j$ backgrounds,
that is, we ignore the contribution from the fakes.
%
For the boosted category, the results are shown in
Table~\ref{table:cutflow4B}, which is the analog of
Table~\ref{table:cutflow} but with only the QCD
$4b$ background taken into account.
%
As we can see, these results indicate that given the similarity of the final states
in signal and background events in these cases, the signal significance is
relatively stable at various stages of the cut-flow.
%
As compared to the case in which all backgrounds are taken into account, we
now get a factor two smaller backgrounds: we conclude that in the boosted category
the effect of the fakes is non-negligible, with their contribution being
comparable to that of the irreducible $4b$ QCD multi-jet background.

Concerning the other categories, we see that that ignoring the fakes can lead to a substantial
distortion of the results.
%
In the intermediate category, the signal significance is now much better, with $S/sqrt{B}$ increasing from
0.5 with all the backgrounds to $1.57$ if only $4b$ are accounted for, a factor 3 improvement.
%
Also the resolved category improves substantially, with signal significance increasing by a factor 2.
%
Therefore, we conclude that a careful modeling of the fakes is very important to truly quantify
the feasibility of Higgs pair production in the $4b$ channel, though for the most
important category, the boosted category, the results are relatively stable.

@@

>>>>

\section{Results for the cut-based analysis}

@@

In this section we discuss the results of the traditional
cut-based analysis, using the analysis strategy presented in the previous
section.
%
We compare our results with other recent related studies,
and in particular we study how the signal significance
is modified if only the $4b$ QCD background is taken into account,
but the $2b2j$ and $jjjj$ backgrounds are neglected.
%
Then in the next section we show how using multivariate techniques
one can substantially improve the signal significance as compared
to the cut-based analysis.

@@

First of all we compare the cross-sections at various
analysis levels for the three categories, for signal and background,
by providing a detailed cut-flow.
%
Here we consider all backgrounds enumerated in Sect.~\ref{mcgeneration},
and below we discuss how results are modified if only the $4b$
multijet background is used.
%
In particular,
we consider the following levels of the cut-flow
\begin{itemize}
\item {\bf C0}: cross-sections at the generator
  level, before any analysis cuts.
\item {\bf C1}:  cross-sections after the basic jet acceptance selection
  cuts, but before $b$-tagging.
\item {\bf C2}: cross-sections after after the $b$-tagging.
\end{itemize}
Note that {\bf C1} already includes the effect of the Higgs mass
window cut, Eq.~(\ref{higgsmasswindow}).
%
Of course at the {\bf C0} level the numbers will be the same
for the three individual categories.

In the following, results are presented for the exclusive
categorisation, as discussed in Sect.~\ref{sec:categorisation}.
%
In Appendix.~\ref{sec:overlap} we comment
interplay of the overlap between the various categories.
%
At each stage of the cut flow, we also provide the number
of events that would be expected at the HL-LHC with
an integrated luminosity of $\mathcal{L}=3000$ fb$^{-1}$,
as well as 
the signal significance $S/\sqrt{B}$ and the signal
over background ratio $S/B$.
%
We emphasize that it is important not only to achieve a good signal
significance, $S/sqrt{B}$, but also a good signal over background ratio $S/B$:
if the latter is too small, a measurement of the background with an infeasible small
systematic uncertainty would be required.

@@

The results for the three categories have been collected in
Table~\ref{table:cutflow}.
%
Let us begin with the discussion of the boosted category, that as we have explained
is the one that benefits from a higher signal significance.
%
We see that after all the cuts, including $b$-tagging,
we end up with almost 200 signal events at the HL-LHC, and
still a substantial background of around $40k$ events.
%
The signal significance is around 1.0 at the end of the
cut-based analysis.
%
While it should have been possible to increase this significance
but using more aggressive cuts, we have refrained doing so
since we prefer this optimisation to per performed by
the MVA.

Note that from the results of Table~\ref{table:cutflow}
it is easy to compute the corresponding numbers
for the end of Run II at the LHC with
$\mathcal{L}_{\rm int}=300$ fb$^{-1}$: in the boosted category,
we have only
19 signal events, and the signal significance drops down to
$S/\sqrt{B}\sim 0.3$.
%
We will discuss in the next section what are the Run II prospects
once we include the effects of the MVA in the analysis, but
it is clear already at this level that, unless rates are
increased by new BSM dynamics, one really needs the full
integrated luminosity of the HL-LHC to be able to observe
the Higgs pair production process.

@@

From the results of Table~\ref{table:cutflow}
we see that after the cut-based analysis, the significance of the Higgs pair production
observation in the $4b$ channel using the boosted topology
is $S/\sqrt{B}=0.99$,
and that the combination
of the boosted, intermediate and resolved categories gives a slightly higher
value, around 1.20.
%
We discuss in the next section how this significance can be enhanced by means
of multivariate analysis.

@@

The feasibility of Higgs pair production at the HL-LHC in different
final-state channels
has been explored various groups~\cite{Baur:2003gp,Barger:2013jfa,
  Baur:2003gpa,Barr:2013tda,Dolan:2013rja,
  Dolan:2012rv,Papaefstathiou:2012qe,Gouzevitch:2013qca,Cooper:2013kia,Wardrope:2014kya,deLima:2014dta}, though
the $4b$ final state has received less attention than other final states,
due to the complexity of disentangling the signal over the large
QCD multijet background.
%
Now we compare with two recent studies that have also studied the
feasibility of SM Higgs pair production in the $4b$ final state,
those of the UCL group~\cite{Wardrope:2014kya} and of the
Durham group~\cite{deLima:2014dta}.
%
In order to perform a meaningful comparison, we will only consider
here the $4b$ QCD and $t\bar{t}$ backgrounds, as was done
in these two studies.

First of all let us briefly summarize these two studies.
%
In the UCL group study~\cite{Wardrope:2014kya} is based
on requiring at least four $b$-tagged $R=0.4$ anti-$k_T$ jets
in the central acceptance with $p_T \ge 40$ GeV, which are
then used to form dijets (Higgs candidates) with
$p_T \ge 150$ GeV, $85 \le m_{\rm dijet} \le 140$ GeV
and $\Delta R \le 1.5$ between the two jets that form
each dijet system.
%
In addition to the basic selection cuts, a large number
of additional variables are combined using a
Boosted Decision Tree (BDT) discriminant.
%
This study considers the $b\bar{b}b\bar{b}$ and
$b\bar{b}c\bar{c}$ QCD multijets as well as
$t\bar{t}$, $Zh$, $t\bar{t}h$ and $hb\bar{b}$.
%
Their final significance is found to the $S/\sqrt{B}=2.1$ at the HL-LHC.

The Durham group study~\cite{deLima:2014dta} requires events
to have two $R=1.2$ C/A jets with $p_T\ge 200$ GeV, with
two $b$-tagged subjets inside each large-$R$ jet with
$p_T \ge$ 40 GeV.
%
To improve the signal over background separation, both the BDRS
method and the Shower Deconstruction (SD)~\cite{Soper:2011cr,Soper:2012pb}
technique are applied.
%
The background considered are QCD $4b$ as well as $Zb\bar{b}$, $hZ$ and
$hW$, but no $t\bar{t}$, $2b2j$ or $4j$.
%
At the HL-LHC, the best performance is obtained by requiring two
SD-tagged large-$R$ jets, which leads to $S/\sqrt{B}\sim 2.1$,
with BDRS similar but slightly inferior performance.
%
Therefore, both the Durham and the UCL groups conclude that a signal
significance $S/\sqrt{B}$ slightly above two can  be obtained
in this channel at the HL-LHC.

Since we find that the $2b2j$ and $4j$ backgrounds cannot
be neglected, and previous works did not considered them,
it is interesting to
study how our results are modified if we consider only the QCD $4b$
multi-jet background, but ignore the $2b2j$ and $4j$ backgrounds,
that is, we ignore the contribution from the fakes.
%
These results are shown in
Table~\ref{table:cutflow4B}, which is the analog of
Table~\ref{table:cutflow} but with only the QCD
$4b$ background taken into account.
%
As we can see, these results indicate that given the similarity of the final states
in signal and background events in these cases, the signal significance is
relatively stable at various stages of the cut-flow.
%
As compared to the case in which all backgrounds are taken into account, we
now get a factor two smaller backgrounds: we conclude that in the boosted category
the effect of the fakes is non-negligible, with their contribution being
comparable to that of the irreducible $4b$ QCD multi-jet background.

Concerning the other categories, we see that that ignoring the fakes can lead to a substantial
distortion of the results.
%
In the intermediate category, the signal significance is now much better, with $S/\sqrt{B}$ increasing from
0.5 with all the backgrounds to $1.57$ if only $4b$ are accounted for, a factor 3 improvement.
%
Also the resolved category improves substantially, with signal significance increasing by a factor 2.
%
Therefore, we conclude that a careful modeling of the fakes is very important to truly quantify
the feasibility of Higgs pair production in the $4b$ channel, though for the most
important category, the boosted category, the results are relatively stable.
%
Moreover, we find that the effect of the multijet fake background is of
the same size of the higher-order QCD corrections to $4b$ production~\cite{Binoth:2009rv}.

@@

In summary, we find that the results of our cut-based analysis are roughly
consistent with the results of previous related studies.
%
As we show next, once the MVA is used, we manage to outperform these previous
works.
